User guide to MSEtool

### 2018-08-13 inst/doc/MSEtool.Rmd
Use tempdir() instead of getwd()

---
title: "User guide to MSEtool"
subtitle: "Development, Testing and Implementation of Management Procedures for Data-Rich Fisheries"
author: "Tom Carruthers (<t.carruthers@oceans.ubc.ca>) 
         Adrian Hordyk  (<a.hordyk@oceans.ubc.ca>),
         Quang Huynh (<q.huynh@oceans.ubc.ca>)"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    toc: true
    number_sections: true 
vignette: >
  %\VignetteIndexEntry{User guide to MSEtool}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

@@

@@

```{r, eval = FALSE}
summary(DD_result)
plot(DD_result, save_figure = TRUE, save_dir = getwd()) # By default, also saves figures in the working directory and HTML browser for future viewing
```

@@

This MP will call `DD_TMB(SR = "Ricker")`.

>>>>

---
title: "User guide to MSEtool"
subtitle: "Development, Testing and Implementation of Management Procedures for Data-Rich Fisheries"
author: "Quang Huynh (<q.huynh@oceans.ubc.ca>), Tom Carruthers (<t.carruthers@oceans.ubc.ca>), 
         Adrian Hordyk (<a.hordyk@oceans.ubc.ca>)"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    toc: true
    number_sections: true 
vignette: >
  %\VignetteIndexEntry{User guide to MSEtool}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

@@

To facilitate a standardized design for data-rich MPs, MSEtool creates new classes to build out the __MP__ class. MSEtool uses functions of class __Assess__ and __HCR__ for an assessment model and harvest control rule, respectively. An __MP__ class function can be made from these functions to be tested in a MSE within the DLMtool framework.

@@

```{r, eval = FALSE}
summary(DD_result)
plot(DD_result, save_figure = TRUE, save_dir = tempdir()) # By default, also saves figures in a temporary directory for viewing through a HTML browser. The directory can be changed to a user's filespace of choice.
```

@@

This MP will call `DD_TMB(..., SR = "Ricker", fix_h = TRUE)`.
